---
title: "Day3_Final_Exercise"
author: "Marcus Thuillier"
date: "9/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading the data
```{r}
library(data.table)
library(lubridate)
library(dplyr)

schools <- fread(here::here("data/nys_schools.csv"), 
                       stringsAsFactors = F)
counties <- fread(here::here("data/nys_acs.csv"), 
                    stringsAsFactors = F)
```

Exploring the data schools
```{r}
str(schools)
head(schools)
schools[schools==-99] <- NA
```

Exploring the data counties
```{r}
str(counties)
head(counties)
summary(counties)
counties[counties==-99] <- NA
```

```{r}

LOW <- counties[county_per_poverty < .10903,]
MEDIUM <- counties[county_per_poverty > .10903 & county_per_poverty < .14929,]
HIGH <- counties[county_per_poverty > .14929,]
```

```{r}
schools <- schools[,Zscore := scale(mean_ela_score + mean_math_score), by = year]

```

```{r}

#setkey(schools, county_name)
#counties[schools]

##I don't know why I couldn't merge the two tables I've tried all the examples we did in class
```

```{r}

```

1. For each county: total enrollment, percent of students qualifying for free or reduced price lunch, and percent of population in poverty


2. For the counties with the top 5 and bottom 5 poverty rate: percent of population in poverty, percent of students qualifying for free or reduced price lunch, mean reading score, and mean math score.



1. The relationship between access to free/reduced price lunch and test performance, at the *school* level.
2. Average test performance across *counties* with high, low, and medium poverty.







